% Timothy B. Hartman - Curriculum Vitae
%
% Copyright (C) 2010 Timothy B. Hartman
%
% LaTeX template Copyright (C) 2004-2010 Jason R. Blevins
%
% from http://jblevins.org/cv.tex
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

% Set your name here
\newcommand\name{Timothy B. Hartman}

\usepackage{geometry}

\usepackage{lastpage}
\usepackage{fancyhdr}
\setlength{\headheight}{14.5pt}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\emph{\name --- cirriculum vit\ae}}
\fancyhead[R]{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\fancypagestyle{plain}{
  \fancyhf{}
  \fancyfoot[C]{Updated: \today}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
}

\usepackage{datetime}
\newdateformat{tbhdate}{\twodigit{\THEDAY}\ \monthname[\THEMONTH] \THEYEAR}
\tbhdate

% Fonts
\usepackage[T1]{fontenc}
\usepackage[urw-garamond]{mathdesign}

\usepackage[plainpages=false]{hyperref}


% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  linkcolor = black,
  citecolor = black,
  filecolor = black,
  pdfauthor = {\name},
  pdfkeywords = {engineering mechanics},
  pdftitle = {\name: Curriculum vitae},
  pdfsubject = {curriculum vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{fancy}
%\markright{\name}
\thispagestyle{plain}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  Department of Engineering Science and Mechanics \\
  Virginia Polytechnic Institute and State University \\
  223 Norris Hall (0219) \\
  Blacksburg, VA 24061
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
% Mobile: (540) 808-3697 \\
  Office: \href{tel:5402313139}{540.231.3139} \\
% Fax: (540) 231-9187 \\
\newcommand{\email}{tbhartman@vt.edu}
  Email: \href{mailto:\email}{\email} \\
  Homepage: \href{http://tbhartman.org}{tbhartman.org}
\end{minipage}

\vspace{12pt}

\rule{\textwidth}{1pt}

%
% Education
%

\section*{Education}

\begin{itemize}
    \item Ph.D. Engineering Mechanics, Virginia Polytechnic Institute and State University, 2013 \textit{(projected)}.
    % Received TBD
    \begin{itemize}
        % \item \textit{Dissertation:}
        %  thesis title goes here
        \item \textit{Committee:}
        Scott W. Case (co-chair), Romesh C. Batra (co-chair), Michael W. Hyer, Robert L. West, and Shane D. Ross.
    \end{itemize}
    \item B.S. Mechanical Engineering, \textit{Cum Laude}, Cedarville University, 2006.
    % Received May ??, 2006
    \begin{itemize}
        \item Passed Fundamentals of Engineering Exam, April 2006.
    \end{itemize}
\end{itemize}

%
% Employment
%

\section*{Employment}

\subsection*{Virginia Tech, Engineering Science and Mechanics}

\begin{itemize}
\item Research Assistant, Scott W. Case, Spring 2009 - present
\item Teaching Assistant, Mechanics of Materials Laboratory, Norman E. Dowling, Fall 2008
    \begin{itemize}
    \item Organized weekly two hour laboratory session including introductory lecture and experiments.  Graded weekly laboratory reports and held office hours.
    \end{itemize}
\end{itemize}

\subsection*{The High School Affiliated with the People's University of China}
%人大附中
\begin{itemize}
\item Teacher, English Physics, August 2007 - June 2008
    \begin{itemize}
    \item Worked with team of sixteen college graduates teaching Chinese students English at a top high school in Beijing, China.  Responsibilities included developing curriculum, creating daily lesson plans, write and grade homework and tests, and building relationships with students out of class.  Taught courses in English physics and English grammar for more than two hundred students each semester.
    \end{itemize}
\end{itemize}

\subsection*{GSE Systems}

\begin{itemize}
\item Systems Engineer, September 2006 - July 2007
    \begin{itemize}
    \item Modeled combined cycle gas turbine power plant mechanical systems for use in a computer simulated control room environment.
    \end{itemize}
\end{itemize}

\subsection*{ITT Industries Aerospace/Communications Division}

\begin{itemize}
\item Manufacturing Engineering Intern, Summer 2005
    \begin{itemize}
    \item Evaluated use of automated optical inspection equipment for in-line inspection of circuit card assembly production.
    \end{itemize}
\end{itemize}

%
% Research
%

\section*{Research}

\subsection*{Journal Articles}
\begin{itemize}
\item Hartman T.B., Hyer M.W., Case S.W.; \textit{Stress Recovery in Composite Laminates.}; AIAA Journal; Accepted 13 August 2011.
\end{itemize}

\subsection*{Conference Proceedings}
\begin{itemize}
\item Hartman T.B., Hyer M.W., Case S.W.; \textit{Stress Recovery in Composite Laminates.}; 52$^{\texttt{nd}}$ AIAA/ASME/ASCE/ASC Structures, Structural Dynamics and Materials Conference, 2011.
\item Hartman T.B., Allen D.W., Case S.W.; \textit{Failure of Spectra Shield UHMWPE Composite Due to Low Velocity Hard Body Impact.}; Proceedings of the 2010 SAMPE Fall Technical Conference.
\end{itemize}

\subsection*{Conference Presentations}
\begin{itemize}
\item \textit{Stress Recovery in Composite Laminates.}
  \begin{itemize}
  \item 2011 AIAA 52$^{\texttt{nd}}$ Fall Technical Conference,
    Denver, CO,
    April 05, 2011.
  \end{itemize}
\item \textit{Failure of Spectra Shield UHMWPE Composite Due to Low Velocity Hard Body Impact.}
  \begin{itemize}
  \item 2010 SAMPE Fall Technical Conference,
    Salt Lake City, UT,
    October 13, 2010.
  \end{itemize}
\end{itemize}

%
% Memberships, Awards, Etc.
%

\section*{Professional Activities}
\begin{itemize}
\item Member, American Institute of Aeronautics and Astronautics, 2011-Present
\item Student Panelist, Virginia Tech Graduate Honor System, 2011-Present
\item Member, Society of Automotive Engineers, 2005-2006
\end{itemize}

\section*{Honors, Awards, \& Fellowships}

\begin{itemize}
\item Jefferson Goblet Award for Outstanding Student Paper, AIAA 52$^{\texttt{nd}}$ SDM Conference, April, 2011
\item NCCAA Sportsmanship Award, Tennis, 2006
%\item NCCAA Scholar-Athlete, Tennis, 2005-2006
\item NAIA Scholar-Athlete, Tennis, 2005-2006
%\item NCCAA All-American, Tennis, 2003-2006
\end{itemize}

\section*{Conferences and Workshops Attended}

\begin{itemize}
\item AIAA 52$^{\texttt{nd}}$ SDM Conference, Denver, CO, April 04-06, 2011
\item SAMPE Fall Conference, Salt Lake City, UT, October 12-14, 2010
\item Graduate Teaching Assistantship Workshop, Virginia Tech, August 2008
\end{itemize}

\medskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}
